---
title: "AdmitDirectlyOOH"
author: "Sulagna Patra"
date: "3/14/2021"
output: html_document
---


```{r Setup and DB Connection, include=FALSE}
source("1_setup_environment.R")
library(dataMaid)
library(DBI)
library(flextable)
```

##Data Analysis for Member_History Table  
```{r,include= FALSE}
con <- DBI::dbConnect(odbc::odbc(), 
                      Driver = "SQL Server", 
                      Server =  "pcnjdevsql02",
                      Database = "PIE_Dev",
                      Trusted_Connection = "True")
dbListTables(con)

dbGetInfo(con)
```

```{r, include= FALSE}
tbl_long_cols_2 <- function(con, table) {
    cols_sorted <-
        odbc::odbcConnectionColumns(con, table) %>%
        dplyr::arrange(column_size) %>%
        pull(name)
    
    dplyr::tbl(con, table) %>%
        dplyr::select(tidyselect::all_of(cols_sorted))
}
AdmitDirectlyOOH<- tbl_long_cols_2(con, "RSPM_AdmitDirectlyOOH")%>%
    collect()

```

#1.1.0 Observing the data structure
#Understanding Number of rows and columns
```{r dataset, rows and column}
dim(AdmitDirectlyOOH)

```

## Initial Information with description of their structure
```{r dataset, parameters}
str(AdmitDirectlyOOH)

```
## Creating a dataframe from the data
```{r}
AdmitDirectlyOOH <- data.frame(AdmitDirectlyOOH)
```
# Number of rows and Cols
```{r}
nrow(AdmitDirectlyOOH)
ncol(AdmitDirectlyOOH)
```
```{r}
names(AdmitDirectlyOOH)
summary(AdmitDirectlyOOH)
```

#Checking data for any missing values
```{r}
colSums(sapply(AdmitDirectlyOOH, is.na))
```


<!--  ```{r} -->
<!-- #length(unique(AdmitDirectlyOOH$ProviderType)) -->
<!-- ``` -->

<!-- # # ProviderType_tb <- ProviderType_tb %>% -->
<!-- # #             arrange(desc(Freq)) -->
<!-- # # ProviderType_tb <-flextable(ProviderType_tb) -->
<!-- # # ProviderType_tb -->
<!-- # ``` -->
<!-- # ## Overall record in 26 unique provider County -->
<!-- # ```{r} -->
<!-- # length(unique(RSPM_DataSet$ProviderCounty)) -->
<!-- # # table(RSPM_DataSet$ProviderCounty,RSPM_DataSet$OOH ) -->
<!-- # ``` -->
<!-- # ```{r, include=FALSE} -->
<!-- # ProviderCounty_tb<-data.frame(table(RSPM_DataSet[,"ProviderCounty"])) -->
<!-- # ProviderCounty_tb <- ProviderCounty_tb %>% -->
<!-- #     arrange(desc(Freq)) -->
<!-- # ProviderCounty_tb <-flextable(ProviderCounty_tb) -->
<!-- # ProviderCounty_tb -->
<!-- # ``` -->
<!-- # ##How many Unique Diagnosis1 -->
<!-- # ```{r} -->
<!-- # length(unique(RSPM_DataSet$Diagnosis1)) -->
<!-- # #table(RSPM_OOH_Claims_History$ProviderCounty) -->
<!-- # ``` -->
<!-- # -->


<!-- # ```{r, include=FALSE} -->
<!-- # # Diagnosis1_tb<- data.frame( table(RSPM_DataSet[,"Diagnosis1"])) -->
<!-- # # Diagnosis1_tb <- Diagnosis1_tb %>% -->
<!-- # #             arrange(desc(Freq)) -->
<!-- # #Diagnosis1_tb -->
<!-- # ``` -->
<!-- # -->
<!-- # ## Find the number of unique member in each Diagnosis1 -->
<!-- # ```{r} -->
<!-- # Tb_Diagnosis1  <-RSPM_DataSet %>% -->
<!-- #     select(Diagnosis1 ,memberid)%>% -->
<!-- #     group_by(Diagnosis1 )%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid)) -->
<!-- # Tb_Diagnosis1 <-Tb_Diagnosis1  %>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # Tb_Diagnosis1 -->
<!-- # ``` -->
<!-- # -->
<!-- # ```{r} -->
<!-- # length(unique(RSPM_DataSet$OOH)) -->
<!-- # ``` -->
<!-- # ## How many unique member in the dataset -->
<!-- # ```{r , function} -->
<!-- # length(unique(RSPM_DataSet$memberid)) -->
<!-- # ``` -->
<!-- # -->
<!-- # #This dataset contains 148199 unique members -->
<!-- # -->
<!-- # ##Distribution of OOH in the dataset -->
<!-- # ```{r} -->
<!-- # tb <-table((RSPM_DataSet$OOH)) -->
<!-- # prop.table(tb)*100 -->
<!-- # -->
<!-- # ``` -->
<!-- # ## how many unique member in OOH pacement catagory -->
<!-- # ```{r} -->
<!-- # OOH_df <- RSPM_DataSet %>% -->
<!-- #     select(OOH,memberid)%>% -->
<!-- #     group_by( OOH)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid))%>% -->
<!-- #     mutate(pct =(dismem_ct/sum(dismem_ct)*100) )%>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # OOH_df -->
<!-- # -->
<!-- # ``` -->
<!-- # ## How many unique member in different age and OOH placement -->
<!-- # -->
<!-- # ```{r} -->
<!-- # OOH_agedf <- RSPM_DataSet %>% -->
<!-- #     select(OOH,memberid,MemberAge,MemberGender,MemberEnrollmentAge,MemberRaceEthnicity)%>% -->
<!-- #     group_by(MemberAge, OOH)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid))%>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # OOH_agedf -->
<!-- # ``` -->
<!-- # ## How many unique member in Each age and OOH placement is 1 -->
<!-- # ```{r} -->
<!-- # OOH_df <- RSPM_DataSet %>% -->
<!-- #     select(OOH,memberid,MemberAge,MemberGender,MemberEnrollmentAge,MemberRaceEthnicity)%>% -->
<!-- #     group_by(MemberAge, OOH)%>% -->
<!-- #     filter(OOH ==1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid))%>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # OOH_df -->
<!-- # -->
<!-- # ``` -->
<!-- # ## Find the unique member in each enrollment age and placed in OOH -->
<!-- # -->
<!-- # ```{r} -->
<!-- # Tb_MemDemo  <-RSPM_DataSet %>% -->
<!-- #     select(MemberEnrollmentAge,OOH,memberid,MemberAge,MemberGender)%>% -->
<!-- #     group_by(MemberEnrollmentAge,OOH )%>% -->
<!-- #     filter(OOH == 1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid)) -->
<!-- # Tb_EnrollAge  <-Tb_MemDemo   %>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # Tb_EnrollAge -->
<!-- # ``` -->
<!-- # ## Unique Member in each gender -->
<!-- # ```{r} -->
<!-- # OOH_Gender  <-RSPM_DataSet %>% -->
<!-- #     select(OOH,memberid,MemberAge,MemberGender)%>% -->
<!-- #     group_by(MemberGender,OOH )%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid)) -->
<!-- # -->
<!-- # OOH_Gender -->
<!-- # ``` -->
<!-- # ## Member EnrollmentAge Vs OOH -->
<!-- # ```{r} -->
<!-- # xtabs( ~ MemberEnrollmentAge+OOH,RSPM_DataSet) -->
<!-- # ``` -->
<!-- # ## Unique Member in each MemberEnrollmentAge with OOH placement -->
<!-- # ```{r} -->
<!-- # OOH_EnrollAge  <-RSPM_DataSet %>% -->
<!-- #     select(OOH,memberid,MemberEnrollmentAge,MemberGender)%>% -->
<!-- #     group_by(MemberEnrollmentAge,OOH )%>% -->
<!-- #     filter(OOH == 1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid))%>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # -->
<!-- # OOH_EnrollAge -->
<!-- # ``` -->
<!-- # ## Age group Vs OOH -->
<!-- # ```{r} -->
<!-- # #xtabs(~ MemberAgeGroup+OOH,data=RSPM_DataSet) -->
<!-- # ``` -->
<!-- # ## Unique Member in each MemberAgeGroup with OOH placement -->
<!-- # ```{r} -->
<!-- # OOH_AgeGr  <-RSPM_DataSet %>% -->
<!-- #     select(OOH,memberid,MemberAgeGroup,MemberGender)%>% -->
<!-- #     group_by(MemberAgeGroup,OOH )%>% -->
<!-- #     filter(OOH == 1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid))%>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # -->
<!-- # OOH_AgeGr -->
<!-- # ``` -->
<!-- # -->
<!-- # -->
<!-- # -->
<!-- # ## Gender vs OOH -->
<!-- # ```{r} -->
<!-- # table(RSPM_DataSet$MemberGender,RSPM_DataSet$OOH) -->
<!-- # ``` -->
<!-- # ## Unique Member in each MemberGender with OOH placement -->
<!-- # ```{r} -->
<!-- # OOH_MemberGender  <-RSPM_DataSet %>% -->
<!-- #     select(OOH,memberid,MemberAgeGroup,MemberGender)%>% -->
<!-- #     group_by(MemberGender,OOH )%>% -->
<!-- #     filter(OOH == 1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid))%>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # -->
<!-- # OOH_MemberGender -->
<!-- # ``` -->
<!-- # -->
<!-- # -->
<!-- # -->
<!-- # ## Race vs OOH -->
<!-- # ```{r} -->
<!-- # # table(RSPM_DataSet$MemberRaceEthnicity,RSPM_DataSet$OOH) -->
<!-- # xtabs(~ MemberRaceEthnicity+OOH, data=RSPM_DataSet) -->
<!-- # ``` -->
<!-- # ## Service Code vs OOH -->
<!-- # ```{r} -->
<!-- # length(unique(RSPM_DataSet$ServiceCode)) -->
<!-- # #xtabs(~ ServiceCode+OOH, data=RSPM_DataSet) -->
<!-- # ``` -->
<!-- # ## Find the number of unique member in each Service code and OOH -->
<!-- # ```{r} -->
<!-- # Tb_ServiceCode  <-RSPM_DataSet %>% -->
<!-- #     select(ServiceCode,OOH,memberid)%>% -->
<!-- #     group_by(ServiceCode,OOH )%>% -->
<!-- #     filter(OOH == 1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid)) -->
<!-- # Tb_ServiceCode <- Tb_ServiceCode   %>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # Tb_ServiceCode -->
<!-- # ``` -->
<!-- # ## Find the number of unique member in each member county and OOH -->
<!-- # ```{r} -->
<!-- # Tb_county  <-RSPM_DataSet %>% -->
<!-- #     select(MemberZipCode,OOH,memberid)%>% -->
<!-- #     group_by(MemberZipCode,OOH )%>% -->
<!-- #     filter(OOH == 1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid)) -->
<!-- # Tb_county  <- Tb_county   %>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # Tb_county -->
<!-- # ``` -->
<!-- # -->
<!-- # ## Find the number of unique member in different diagnosis1 who are placed in OOH -->
<!-- # -->
<!-- # ```{r} -->
<!-- # Tb_Diagnosis1  <-RSPM_DataSet %>% -->
<!-- #     select(Diagnosis1,OOH,memberid)%>% -->
<!-- #     group_by(Diagnosis1,OOH )%>% -->
<!-- #     filter(OOH == 1)%>% -->
<!-- #     summarise(dismem_ct=n_distinct(memberid)) -->
<!-- # Tb_Diagnosis1  <- Tb_Diagnosis1   %>% -->
<!-- #     arrange(desc(dismem_ct)) -->
<!-- # Tb_Diagnosis1 -->
<!-- # ``` -->
<!-- # -->
<!-- # ## Is there any significant relation between Age/Race/gender with OOH Placement -->
<!-- # ```{r, include=FALSE} -->
<!-- # #  model1 <-glm(OOH ~ MemberAge+MemberGender+MemberRaceEthnicity,data=RSPM_DataSet, family=binomial()) -->
<!-- # # summary(model1) -->
<!-- # ``` -->
<!-- # -->
<!-- # ##ggplot Gender Vs OOH -->
<!-- # ```{r} -->
<!-- # df_Gender <- RSPM_DataSet%>% -->
<!-- # -->
<!-- #     group_by(MemberGender,OOH )%>% -->
<!-- #     summarise(count=n()) -->
<!-- # df_Gender <- data.frame(df_Gender) -->
<!-- # plot_gender<- ggplot(data=df_Gender,aes(x =MemberGender,y=count,fill = as.factor(OOH)))+ geom_bar(stat="identity",position = position_dodge())+theme_minimal() -->
<!-- # plot_gender -->
<!-- # ``` -->
<!-- # ##ggplot Race Vs OOH -->
<!-- # ```{r} -->
<!-- # df_Race <- RSPM_DataSet%>% -->
<!-- # -->
<!-- #     group_by(MemberRaceEthnicity,OOH )%>% -->
<!-- #     summarise(count=n()) -->
<!-- # df_Race <- data.frame(df_Race) -->
<!-- # plot_Race<- ggplot(data=df_Race,aes(x =MemberRaceEthnicity,y=count,fill = as.factor(OOH)))+ geom_bar(stat="identity",position = position_dodge())+theme_minimal() -->
<!-- # plot_Race -->
<!-- # ``` -->
<!-- # ##ggplot AgeGr Vs OOH -->
<!-- # ```{r} -->
<!-- # df_AgeGr <- RSPM_DataSet%>% -->
<!-- # -->
<!-- #     group_by(MemberAgeGroup,OOH )%>% -->
<!-- #     summarise(count=n()) -->
<!-- # df_AgeGr <- data.frame(df_AgeGr) -->
<!-- # plot_AgeGr<- ggplot(data=df_AgeGr,aes(x =MemberAgeGroup,y=count,fill = as.factor(OOH)))+ geom_bar(width=1,stat="identity",position = position_dodge())+theme_minimal() -->
<!-- # plot_AgeGr -->
<!-- # ``` -->
 ##Cohort
 ##How Many unique member Admit directly to OOH

```{r}
length(unique(AdmitDirectlyOOH$memberid))
# OOH_df <- AdmitDirectlyOOH %>%
#     select(OOH,memberid)%>%
#     group_by( OOH)%>%
#      summarise(dismem_ct=n_distinct(memberid))%>%
#      arrange(desc(dismem_ct))
#  OOH_df

```

# 1682 are admitted directly to OOH without any previous Services

## Clinical Profile
## a. Diagnosis
```{r}
OOH_diag <- AdmitDirectlyOOH %>%
     select(memberid,Diagnosis1,OOH)%>%
     group_by(memberid)%>%
     filter( OOH== 1)%>%
     summarise(disDiag=n_distinct(Diagnosis1))%>%
     arrange(desc(disDiag))
 OOH_diag

```
 
##Converting ICD10 code to SDoH Catagories
```{r,SDoH Diagnosis,include= FALSE}
AdmitDirectlyOOH<- data.frame(AdmitDirectlyOOH)
AdmitDirectlyOOH$Diagnosis1[AdmitDirectlyOOH$Diagnosis1 == 'Z550' |AdmitDirectlyOOH$Diagnosis1 == 'Z551'|AdmitDirectlyOOH$Diagnosis1 == 'Z558'|AdmitDirectlyOOH$Diagnosis1 == 'Z559'] <-"Education"
AdmitDirectlyOOH$Diagnosis1[AdmitDirectlyOOH$Diagnosis1 >= 'Z590' &AdmitDirectlyOOH$Diagnosis1 <= 'Z599'] <-"Housing and Economic"
AdmitDirectlyOOH$Diagnosis1[AdmitDirectlyOOH$Diagnosis1 >= 'Z602' &AdmitDirectlyOOH$Diagnosis1 <= 'Z605' |
                           AdmitDirectlyOOH$Diagnosis1 == 'Z600' |
                            AdmitDirectlyOOH$Diagnosis1 == 'Z608' |
                            AdmitDirectlyOOH$Diagnosis1 == 'Z609']<-"Social Environment"

AdmitDirectlyOOH$Diagnosis1[
    AdmitDirectlyOOH$Diagnosis1 == 'Z734' | AdmitDirectlyOOH$Diagnosis1 == 'Z7389' |
        AdmitDirectlyOOH$Diagnosis1 == 'Z733' | AdmitDirectlyOOH$Diagnosis1 == 'Z739' |
        AdmitDirectlyOOH$Diagnosis1 == 'Z659' |
        AdmitDirectlyOOH$Diagnosis1 == 'Z658']<-"Stress"
AdmitDirectlyOOH$Diagnosis1[AdmitDirectlyOOH$Diagnosis1 >= 'Z650' & AdmitDirectlyOOH$Diagnosis1 <= 'Z655'] <-"Experiences Crime,Violence,Judicial"

AdmitDirectlyOOH$Diagnosis1[AdmitDirectlyOOH$Diagnosis1 == 'Z6221' | AdmitDirectlyOOH$Diagnosis1 == 'Z6222' |
                            AdmitDirectlyOOH$Diagnosis1 == 'Z6229' |
                            AdmitDirectlyOOH$Diagnosis1 == 'Z62810' |
                            AdmitDirectlyOOH$Diagnosis1 == 'Z62811' |
                            AdmitDirectlyOOH$Diagnosis1 == 'Z62812' |
                            AdmitDirectlyOOH$Diagnosis1 =='Z62819']<-"Upbringing"

```
```{r}
tb_SDoH<- AdmitDirectlyOOH %>%
    select(Diagnosis1,memberid )%>%

    filter(AdmitDirectlyOOH$Diagnosis1 %in% c('Upbringing','Experiences Crime,Violence,Judicial','Stress','Social Environment','Housing and Economic','Education'))
tb_SDoH

length(unique(tb_SDoH$memberid))

tb_SDoH_diag<-
    tb_SDoH %>% 
    group_by(Diagnosis1)%>%
    summarise(disMem=n_distinct(memberid))%>%
    arrange(desc(disMem))

tb_SDoH_diag

```
## 16 unique enrollees are related to SDoH diagnosis
##Stress	11	
##Housing and Economic	4	
##Experiences Crime,Violence,Judicial	1
 
 
# Demographic
# Race
```{r}
df_Race <- AdmitDirectlyOOH%>%
          group_by(MemberRaceEthnicity )%>%
     summarise(count=n_distinct(memberid))
 df_Race 
```
##Menber Gender
```{r}
df_Gender <- AdmitDirectlyOOH%>%
          group_by(MemberGender )%>%
     summarise(count=n_distinct(memberid))
 df_Gender 
```

```{r}
df_RaceVsGender <- AdmitDirectlyOOH%>%
          group_by(MemberRaceEthnicity,MemberGender )%>%
     summarise(count=n_distinct(memberid))
 df_RaceVsGender
 
df_RaceVsGender<- as.data.frame(df_RaceVsGender)
 plot_RaceVsGender<- ggplot(data=df_RaceVsGender,aes(x =MemberRaceEthnicity,y=count,fill =as.factor(MemberGender)))+ geom_bar(stat="identity",position = position_dodge())+ggtitle("Plot of Race With Gender") 
 plot_RaceVsGender
```
##member Age
```{r}
df_MemberAge <- AdmitDirectlyOOH%>%
          group_by(MemberAge )%>%
     summarise(count=n_distinct(memberid))%>%
       arrange(desc(count))
 df_MemberAge
```
##member Age Group
```{r}
df_MemberAgeGroup <- AdmitDirectlyOOH%>%
          group_by(MemberAgeGroup )%>%
     summarise(count=n_distinct(memberid))%>%
       arrange(desc(count))
 df_MemberAgeGroup
```
##member Enrollment Age 
```{r}
df_MemberEnrollAge <- AdmitDirectlyOOH%>%
          group_by(MemberEnrollmentAge )%>%
     summarise(count=n_distinct(memberid))%>%
       arrange(desc(count))
df_MemberEnrollAge
```
##member Enrollment Age Group
```{r}
df_MemberEnrollAgeGr <- AdmitDirectlyOOH%>%
          group_by(MemberEnrollmentAgeGroup )%>%
     summarise(count=n_distinct(memberid))%>%
       arrange(desc(count))
df_MemberEnrollAgeGr
```

##Zipcode Of Residence
```{r}
df_MemberZipcode <- AdmitDirectlyOOH%>%
          group_by(MemberZipCode )%>%
          summarise(count=n_distinct(memberid))%>%
          arrange(desc(count))
df_MemberZipcode
```

 
# ## Service Profile
# ##Number of Admission to OOH for each enrolled
```{r}
df_admit<- AdmitDirectlyOOH%>%
           group_by(memberid )%>%
           summarise(count=n_distinct(admitdate))%>%
           arrange(desc(count))
df_admitdate <- data.frame(df_admit)
df_admitdate
```
